---
title: "project-model-evaluation"
author: "Madhuri Kalani"
date: "May 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Loading the Project

The first step of model evaluation is to load the project. It includes installing all the necessary libraries and data munging to prepare the training and test data sets, feature selection.

```{r p0, echo =FALSE, warning=FALSE, include=FALSE}

setwd("C:/Users/akash/Documents/Madhuri stuff/Data_Science_Intro_R/Ad_Fraud_Detection")

library('ProjectTemplate')
load.project()

library('caret')


```

## Training Model using Caret

The caret package in R provides a powerful framework for classification.
  Logistic regression
  SVM Radial
  Random Forest
  Tree Rpart
  Stochastic Gradient Boosting (Generalized Boosted Modeling)


```{r e4, echo=FALSE, warning = FALSE}


train_control <- trainControl(method="cv", number=3)

#01
model_glm <- train(as.factor(is_attributed)~app + channel + ip +device + os + click_time, data=df.train, method="glm", trControl=train_control)

# 02
model_svm <- train(as.factor(is_attributed)~app + channel + ip +device + os + click_time, data=df.train, method="svmRadial", preProc=c("center", "scale"), trControl=train_control, fit=FALSE)

#03
model_rf <- train(as.factor(is_attributed)~app + channel + ip +device + os + click_time, data=df.train, method="rf", trControl=train_control)

#04
model_rpart <- train(as.factor(is_attributed)~app + channel + ip +device + os + click_time, data=df.train, method="rpart", trControl=train_control)

#05
model_gbm <- train(as.factor(is_attributed)~app + channel + ip +device + os + click_time, data=df.train, method="gbm", trControl=train_control, verbose=FALSE)

```
## Summary of Models trained
```{r e1, echo=FALSE, warning = FALSE}
# Combining Results

results <- resamples(list(Logistic=model_glm,SVM=model_svm,Rpart=model_rpart,RandomForest=model_rf,GBM=model_gbm))

# summarize Results and Table comparison
summary(results)
```
## Result: 
```{r e0, echo=FALSE, warning = FALSE}
#Top Performing Models
bwplot(results)

```

### As per the result, the best performing models are rpart and GBM. I will create a R Package which will predict the results using model object.

