---
title: "AdFraudClick_Detection"
author: "Madhuri Kalani"
date: "April 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ad_Fraud_Clicks_Detection

The objective is to predict whether a user will download an application after clicking a mobile advertisement.

Looking at the data it looks like a classification problem that outputs two classes. 
The training data and test data consists of 184 million and 1.8 million rows respectively. 
Each row of training data contains a click record, with the following features:

1. ip: ip address of click.
2. app: app id for marketing.
3. device: device type id of user mobile phone (e.g., iphone 6 plus, huawei mate 7, etc.)
4. os: os version id of user mobile phone
5. channel: channel id of mobile ad publisher
6. click_time: timestamp of click (UTC)
7. attributed_time: if user download the app for after clicking an ad, this is the time of the app download
8. is_attributed: the target that is to be predicted, indicating the app was downloaded (1= app downloaded, 0= not downloaded)

Please note that ip, app, device, os, and channel are encoded. 

Currently, I am beginning my analysis with 1 million rows of training data.

The test data is similar, with the following
differences:
1. click_id: reference for making predictions
2. is_attributed: not included

### Step 1: Loading the Project and training data.
```{r ch1, echo=FALSE, warning=FALSE,message=FALSE}
getwd()
setwd("~/Ad_Fraud_Detection")
library('ProjectTemplate')
load.project()
head(as.data.frame(train.sample))

```

### Step 2: The training data contains 8 variables as shown above. I will be adding few more columns to the training data.
#### Showing Structure and Summary of the training dataset
```{r ch2, echo=FALSE,warning=FALSE,message=FALSE}
train.sample$click_time <- as_datetime(train.sample$click_time)
train.sample$click_hour <- hour(train.sample$click_time)
train.sample$click_day <- weekdays(train.sample$click_time)
train.sample$click_month <- month(train.sample$click_time)
str(train.sample)
## Summary
summary(train.sample)
```
### Step 3: Finding correlation between columns in the training data set.

```{r ch6, echo=FALSE,warning=FALSE,message=FALSE}

M<-cor(train.sample[1:5])
head(round(M,2))
library('corrplot')
corrplot(M, method="color")
```

### Step 4: Building a series of histogram to see the number of times an ip address, app, os, device and channel v alues have been used
```{r ch3, echo=FALSE,warning=FALSE,message=FALSE}
library(ggplot2)
ggplot(data = melt(train.sample[,c(1:5)]), mapping = aes(x = value)) + 
    geom_histogram(bins = 20) + facet_wrap(~variable, scales = 'free_x') + ggtitle(paste("Histogram tells the ",subtitle="number of times an ip, app, os, device and channel values have been used"))

```

### Step 5: Coercing the dataset and making independent variables as factors
```{r ch4, echo=FALSE,warning=FALSE,message=FALSE}
  #Coerce the app column as Factor
train.sample$app <- as.factor(train.sample$app)
#Coerce the ip column as Factor
train.sample$ip <- as.factor(train.sample$ip)
#Coerce the device column as Factor
train.sample$device <- as.factor(train.sample$device)
#Coerce the os column as Factor
train.sample$os <- as.factor(train.sample$os)
#Coerce the channel column as Factor
train.sample$channel <- as.factor(train.sample$channel)
#Coerce the ip column as Factor
train.sample$ip <- as.factor(train.sample$ip)
str(train.sample)
```

### Step 6: Checking how many times the app has been downloaded on hourly basis
```{r ch5, echo=FALSE,warning=FALSE,message=FALSE}
  #Coerce the app column as Factor
tbl <- with(train.sample, table( is_attributed,click_hour))

barplot(tbl, beside = TRUE, legend = TRUE, main= "Hourly Click Frequency")

```


### Step 7: As my analysis continues, I will be building KNN and logistic regression models to find out the actual number of app downloads. 

### I will also be trying other models before final selection and fitting the model into the test data.



```{r ch7, echo=FALSE,warning=FALSE,message=FALSE}

```

##### ---------------------------------------------------------------------------------------------work in progress--------------------------------------------






